---
title: "U.S.Census"
author: "Pat Healy"
date: "9 May 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
#Steps that we want to take
1)Load our API Key

2)Load the census package

3)Query 'hitech' data to see what variables we want to use.
The information for hitech is at https://api.census.gov/data.html
You might be interested in U.S. Exports by Advanced Technology Code
The API query for advanced technology is 'timeseries/intltrade/exports/hitech'

4) Add those varialbes into a query

5) Find out what euro countries we can query 




```{r}
# Add key to .Renviron
#Sys.setenv(CENSUS_KEY=YOURKEYHERE)
# Reload .Renviron
#readRenviron("~/.Renviron")
# Check to see that the expected key is output in your R console
#Sys.getenv("CENSUS_KEY")
```


```{r}
library(censusapi)
```

```{r}
apis <- listCensusApis()
View(apis)
```

```{r}
trade_vars <- listCensusMetadata(name = "timeseries/intltrade/exports/hitech", 
    type = "variables")
head(trade_vars)
```
Variables that may be of interest:

COMM_LVL  '4-character Aggregation Levels for Commodity'
YEAR  '4-character Year'
CTY_NAME  '50-character Country Name'
HITECH_DESC '40-character Hi-Tech Description'
HITECH  '2-character HITECH Code'
CTY_CODE '4-character Country Code'
VES_VAL_YR '15-digit Year-to-Date Vessel Value'
AIR_VAL_YR  '15-digit Year-to-Date Air Value'

##Successful Query!!

```{r}
hitech<- getCensus(name = "timeseries/intltrade/exports/hitech",
    vars = c("HITECH_DESC", "CTY_CODE", "VES_VAL_YR", "AIR_VAL_YR"),
    time = 2015)
```


#how to search for apis with a keyword that you want in the list of API's
Try out different version of capitals as well. alternativley you can make evrything lower case. 
```{r}
library(dplyr)
library(data.table)
trial <- apis[apis$title %like% "Tech", ]

#this gives us two results Exports and Imports


```


