---
title: "trade"
author: "Pat Healy"
date: "7 May 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
Some notes for Donna about the comtradr API for technology/electonic equipment. 

-Install the package comtradr
```{r}
library(comtradr)
```

Find information about the codes at "https://unstats.un.org/unsd/tradekb/Knowledgebase/50039/UN-Comtrade-Reference-Tables"

For this example we were interested in: 
"Electrical machinery and equipment and parts thereof; sound recorders and reproducers; television image and sound recorders and reproducers, parts and accessories of such articles as a commodity. "

The code for this is "85"
To find the EU trade partners we get a list of EU countries from:
https://europa.eu/european-union/about-eu/countries_en

*note* The limit to trade parnters that can be queried at the same time is 5. We therefore have to split this list up into 5 lists. 

to do that we can iterate over the list below 6 times and create a function to run each list. If you get the stage of needing to do that let me know!
```{r}
#Creating eu countries as a character vector
eu<- c("Austria",	"Italy",
"Belgium",	"Latvia",
"Bulgaria",	"Lithuania",
"Croatia",	"Luxembourg",
"Cyprus",	"Malta",
"Czechia",	"Netherlands",
"Denmark",	"Poland",
"Estonia",	"Portugal",
"Finland",	"Romania",
"France",	"Slovakia",
"Germany",	"Slovenia",
"Greece",	"Spain",
"Hungary",	"Sweden",
"Ireland"	)
```


```{r}
#this code searches for electronic equipment traded between USA and France, with export, import and re-export as the trae categories. This includes all years dating back until 1991. 
code <- c("85")
df <- ct_search(reporters = "USA", 
               partners = c("France"), 
               trade_direction = "all", 
               commod_codes = code)
```

